Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
brushing up intro.
improving intro.

%%%% Describe the problem.
\begin{quote}
    TBD: Important points we want to say about BDD:
    \begin{itemize}
        \item
            All behavior should be documented, together with some
            \emph{evidence} for that behavior.
        \item
            \emph{Behavior driven development (BDD)} approaches
            \emph{test-driven development (TDD)} and \emph{acceptance
            test-driven development (ATDD)} with a new terminology and
            mindset.  For the purpose of this paper we only focus on
            the TDD aspect of BDD.
        \item
            Automating things, and continuous integration~\cite{ci} is an important
            aspect of BDD.
        \item
            BDD uses expectations instead of assertions
    \end{itemize}
\end{quote}

@@

\begin{quote}
    TBD: Important points we want to say here:
    \begin{itemize}
        \item
            We use Doctest and Hspec to document behavior.
            (in contrast to other communities)
        \item
            Some features are missing from both, Doctest and
            Hspec.
        \item
            We extend them accordingly, and show how they can be used
            in combination to design, document and test Haskell code.
    \end{itemize}
\end{quote}

In this paper, we explore how to apply BDD to Haskell.
We brought a test method from other programming language community and
integrated it with a Haskell-original test method.
In particular, we introduced Doctest~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck} as a BDD tool.
We also make use of Hspec inspired by RSpec~\cite{rspec} for
BDD in Haskell.

@@

\item
    Introduce a set of combinators to set expectations about
    \emph{code examples} for use with Hspec.

\item
    Improve CI support for Doctest and Hspec

@@

\noindent Our Doctest implementation
can be used for design, documentation and automatic testing.
We hope that this kill-three-birds-with-one-stone aspect
motivates Haskellers to write test code.

@@

\begin{quote}
    \emph{talk about CI}
\end{quote}

>>>>

%%%% Describe the problem.

@@

In this paper, we explore how to apply BDD to Haskell.
BDD approaches
TDD and acceptance test-driven development (ATDD)
with a new terminology and mindset. 
For the purpose of this paper we only focus on the TDD aspect of BDD.

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.
for this purpose, 
we brought a test method from other programming language community and
extended missing features.
In particular, we introduced Doctest~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck}
for user documentation.
For code documentation, we also make use of Hspec inspired by RSpec~\cite{rspec}
and we proposed some combinators to it.

Automating such as test discovery and continuous integration (CI) ~\cite{ci} 
is an important aspect of BDD. TBD: need to say somting.

@@

\item
    Introduce a set of combinators to set expectations about
    \emph{code examples} for use with Hspec. (Section \ref{sec:for-developers})

\item
    Improve CI support for Doctest and Hspec (Section \ref{sec:TBD})

@@

\noindent Our BDD procedure
can be used for design, documentation and automatic testing.
We hope that this kill-three-birds-with-one-stone aspect
motivates Haskellers to write test code.

\begin{quote}
    TBD: Important points we want to say about BDD:
    \begin{itemize}
        \item
            BDD uses expectations instead of assertions
    \end{itemize}
\end{quote}

@@
